Untitled

### 2021-08-31 src/new_economic_parameters.Rmd
RF done by oversampling.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
source("economic_effect_functions.R")
source("article_figures_functions.R")
library(knitr)
library(tidyverse)
save_figs = TRUE
save_tables = FALSE
dir <- "~/FRCBS/interval-sims/src/new_cost_parameters"
fig_path <- dir
table_path <- dir
all_results_filename <- sprintf("%s/raw-data-2021-08-27.tsv", dir)
compute=FALSE
```

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
source("economic_effect_functions.R")
source("article_figures_functions.R")
library(knitr)
library(tidyverse)
save_figs = FALSE
#save_tables = FALSE
dir <- "~/FRCBS/interval-sims/src/new_cost_parameters"
fig_path <- dir
table_path <- dir
all_results_filename <- sprintf("%s/raw-data-2021-08-31.tsv", dir)
compute=FALSE
```
